\chapter{Mechanical Systems}

\section{Introduction}
The Mechanical Department of the Hyperloop team is crucial for the design, development, and implementation of the mechanical systems within the Hyperloop pod. This department focuses on creating innovative solutions to achieve optimal performance, safety, and reliability in the pod's operation. It is responsible for the design and engineering of key mechanical components, including the chassis, suspension, braking systems, and aerodynamics.\\
\\
Chassis: This subdepartment is responsible for designing the pod's leightweight frame or skeleton. The chassis is the foundation that supports all other mechanical components, ensuring they work in harmony. It's engineered to be robust yet lightweight, balancing structural integrity with performance efficiency.

Suspension: The suspension team focuses on the system that connects the chassis to the tracks, absorbing vibrations and shocks to maintain stability during high-speed travel. Their work is crucial for the pod's handling and ride quality.

Braking: Essential for safety and control, the braking subdepartment designs systems to decelerate the pod efficiently. This involves selecting materials and mechanisms that ensure reliable and effective stopping power, considering the pod's high-speed nature.

Aerodynamics: This group works on optimizing the pod's shape and surface to minimize air resistance, which is vital for achieving high speeds and efficient energy use. Their work includes designing the pod's external shell and analyzing airflow to enhance performance.\\
\\
Each subdepartment plays a critical role in the pod's overall design and function, working together to tackle the unique challenges of Hyperloop technology. Their collaborative efforts ensure the pod is safe, efficient, and ready to redefine high-speed transportation.

\input{texfiles/mech/chassis.tex}

\input{texfiles/mech/suspension.tex}

\input{texfiles/mech/friction_braking.tex}

\input{texfiles/mech/magnetic_braking.tex}

\input{texfiles/mech/aerodynamics.tex}





\newpage
